Improving the portuguese hyphenation rules

### 2024-07-01 article/hyphenpatches.tex
fix #53
fix #54
fix #55

\refstepcounter{numberRulesGroups}\item\label{rulegrp_t2} rule: \texttt{.t2} -- tsunami, tzarista

@@

\refstepcounter{numberRulesGroups}\item\label{rulegrp_proi} rule: \texttt{pro1i1b} -- proibição

@@

\refstepcounter{numberRulesGroups}\item\label{rulegrp_aa} rule: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{í1o}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1â}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  \emph{abraâmico}, \emph{abraão}, \emph{aéreo}, \emph{país}, \emph{caótico}, \emph{faraônico}, \emph{saúde}, \emph{balneário}, \emph{oceânico}, \emph{campeã}, \emph{feérico}, \emph{veêm}, \emph{veículo}, \emph{teórico}, \emph{napoleônico}, \emph{conteúdo}, \emph{néon}, \emph{diário}, \emph{região}, \emph{soviético}, \emph{iídiche}, \emph{periódico}, \emph{feiura}, \emph{viúva}, \emph{maníaco}, \emph{íon}, \emph{razoável}, \emph{joão}, \emph{poético}, \emph{boêmia}, \emph{heroísmo}, \emph{alcoólico}, \emph{usuário}, \emph{itapuã}, \emph{lituânia}, \emph{suécia}, \emph{cauê}, \emph{suíça}, \emph{flúor} \\
exception: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2ã}, \texttt{1qu2â}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, -- \emph{jaraguá}, \emph{saguão}, \emph{alguém}, \emph{português}, \emph{linguística}, \emph{aquático}, \emph{camaquã}, \emph{equânime}, \emph{inquérito}, \emph{sequência}, \emph{química} 
% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary

>>>>

\refstepcounter{numberRulesGroups}\item\label{rulegrp_t2} rule: \texttt{.t2} -- \emph{tsunami}, \emph{tzarista}

@@

\refstepcounter{numberRulesGroups}\item\label{rulegrp_proi} rule: \texttt{pro1i1b} -- \emph{proibição}

@@

\refstepcounter{numberRulesGroups}\item\label{rulegrp_aa} rule: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{í1o}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1â}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  \emph{abraâmico}, \emph{abraão}, \emph{aéreo}, \emph{país}, \emph{caótico}, \emph{faraônico}, \emph{saúde}, \emph{balneário}, \emph{oceânico}, \emph{campeã}, \emph{feérico}, \emph{preênsil}, \emph{veículo}, \emph{teórico}, \emph{napoleônico}, \emph{conteúdo}, \emph{néon}, \emph{diário}, \emph{região}, \emph{soviético}, \emph{iídiche}, \emph{periódico}, \emph{feiura}, \emph{viúva}, \emph{maníaco}, \emph{íon}, \emph{razoável}, \emph{joão}, \emph{poético}, \emph{boêmia}, \emph{heroísmo}, \emph{alcoólico}, \emph{usuário}, \emph{itapuã}, \emph{lituânia}, \emph{suécia}, \emph{cauê}, \emph{suíça}, \emph{flúor} \\
exception: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2ã}, \texttt{1qu2â}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, -- \emph{jaraguá}, \emph{saguão}, \emph{alguém}, \emph{português}, \emph{linguística}, \emph{aquático}, \emph{camaquã}, \emph{equânime}, \emph{inquérito}, \emph{sequência}, \emph{química} 
% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary
